#Analysising Brain Data


Here we are interested in analysing the brain data from our paper. The first step is to upload the data:

```{r}
dat<-read.table("/home/unix/ssimmons/FivePrime/GithubCode/FivePrime/AnalysingBrain/data/Brain_Data.bed",header=T)
head(dat)
```

#Comparing 5' bias between samples (Figure 6b)

We can then import the code. Note that this code was used for Figure 6b and 6c to get the corresponding p-value.

```{r}
source("/ahg/regevdata/projects/FiveprimeRNA/seanken/GithubCode/FivePrime/AnalysingBrain/Pval.R")
```

We are then able to calculate the normalized change in 5' to 3' bias, the p-value, and standard deviation and errors. For example, if we want to compare the invitro neurons (H66) to the fetal frontal cortex data, we get:

```{r}
pv=getPval(dat,"H66","Fetal_Frontal")
print(pv)
```

This is testing if H66 is more 5' than fetal frontal cortex. Note the results are close, but not quite identical to those in the paper--this is due to the random downsampling step when calling peaks.


#Comparing number expressed peaks between samples (Figure 6c)

If we aren't interested in comparing 5' bias between samples but instead of comparing the number of TSS used per Gene, we would run:

```{r}
pv=getPval(dat,"H66","Fetal_Frontal",normed=F,scor_test="num")
print(pv)
```

This is testing the hypopthesis that H66 has less active TSS than the fetal frontal cortex.
i

#Performing DE on five prime data (Figure 5a)

We are also interested, for a given pair of regions, finding genes that are different between them. As such, for each gene with >1 peaks and >100 reads mapped to it, we want to test if there is a difference in proporition between the two samples for usage. Note there is only one biological replicate per tissue, so the reults should be taken with a grain of salt (similiar warning applies to the above results).

To do this, we first load the fisher exact code used:

```{r}
source("fishers_exact.R")
```

In order to run this, we need to rename the columns so that all columns that contain count data begin with "PR_". We also add an alternative name column that has extra information about each peak:

```{r}
dat$Name = paste(dat$Gene, dat$Position_in_Gene, dat$Number_Peaks_in_Gene, sep="_")
dat <- dat[, c(ncol(dat), (1:ncol(dat))[-ncol(dat)])]
colnames(dat)[8:15] = paste0("PR_",colnames(dat)[8:15])
head(dat)
```

With the table properly formatted, we can now run the test for all pairs of samples and all genes:

```{r}
res=calculate_all(dat)
head(res)
```

This can then be used to find interesting genes!
